---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-05"
output: html_document
---

## Dataset: Übersicht über Wirtschaftsbereiche/Branchen

Übersicht über Wirtschaftsbereiche / Branchen für die im Gemeinsamen Tarifregister Berlin und Brandenburg Tarifverträge vorliegen, aus denen Auskunft erteilt werden kann.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenarbeitbeschaeftigungtarifregistertarifinformationenwirtschaftsbereiche)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/arbeit/beschaeftigung/tarifregister/tarifinformationen/wirtschaftsbereiche/)

Auto generated R starter code for data set 011b91c4-e5f0-4f86-91ad-aa2e8a92bf34.

## Metadata

- **Maintainer** `Anette Leiner`
- **Maintainer_email** `tarifregister@senias.berlin.de`
- **Tags** `['simplesearch', 'tarifregister_tarifauskunft_tarifvertrag_wirtschaftsbereiche_branchen_berlin_brandenburg']`
- **Date_released** `2016-05-24`
- **Metadata_created** `2019-03-26T16:23:33.494360`
- **Metadata_modified** `2019-12-19T13:22:02.167297`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 011b91c4-e5f0-4f86-91ad-aa2e8a92bf34

df <- read.csv('https://www.berlin.de/sen/arbeit/beschaeftigung/tarifregister/tarifinformationen/wirtschaftsbereiche/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Anette Leiner | tarifregister@senias.berlin.de
