---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-20"
output: html_document
---

## Dataset: Publikationen des Bezirksamtes Tempelhof-Schöneberg von Berlin

Publikationen des Bezirksamtes Tempelhof-Schöneberg

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebatempelhofschoenebergservicepublikationensimplesearch)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-tempelhof-schoeneberg/service/publikationen/simple-search/)

Auto generated R starter code for data set 051d1015-b570-4628-be51-9bab795c7a28.

## Metadata

- **Maintainer** `Cornelia Stolt`
- **Maintainer_email** `publikationen@ba-ts.berlin.de`
- **Tags** `['broschüre', 'flyer', 'heft', 'infos', 'simplesearch']`
- **Date_released** `2015-11-05`
- **Metadata_created** `2016-02-18T20:59:54.039916`
- **Metadata_modified** `2024-08-07T16:18:56.370031`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 051d1015-b570-4628-be51-9bab795c7a28

df <- read.csv('https://www.berlin.de/ba-tempelhof-schoeneberg/service/publikationen/simple-search/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Cornelia Stolt | publikationen@ba-ts.berlin.de
