---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-07"
output: html_document
---

## Dataset: Doppelhaushalt 2024/2025

Haushaltsdaten des Landes Berlin für die Haushaltsjahre 2024/2025

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=doppelhaushalt-2024-2025-1418812)<br>
[Direct link by Datenrubrik for dataset](https://www.berlin.de/sen/finanzen/haushalt/doppelhaushalt/artikel.1236946.php)

Auto generated R starter code for data set 054014ca-d59d-4a97-83e9-7adc12737227.

## Metadata

- **Maintainer** `Seda Hommens`
- **Maintainer_email** `onlineredaktion@senfin.berlin.de`
- **Tags** `['Haushaltsplan', 'Landeshaushalt']`
- **Date_released** `2024-02-19`
- **Metadata_created** `2024-02-20T13:08:10.465140`
- **Metadata_modified** `2024-03-15T11:02:52.294294`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 054014ca-d59d-4a97-83e9-7adc12737227

df <- read.csv('https://www.berlin.de/sen/finanzen/service/daten/csv-opendata_doppelhaushalt_2024_2025.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Seda Hommens | onlineredaktion@senfin.berlin.de
