---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-25"
output: html_document
---

## Dataset: Angebote des Bezirksamts zur Unterst端tzung von Fl端chtlingen



    Angebote des Bezirksamts zur Unterst端tzung von Fl端chtlingen
    im Bezirk Friedrichshain-Kreuzberg
  


[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebafriedrichshainkreuzbergaktuellesfluechtlingshilfeangebotedesbezirksamts)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/ba-friedrichshain-kreuzberg/aktuelles/fluechtlingshilfe/angebote-des-bezirksamts/)

Auto generated R starter code for data set 0724dd59-0d86-43b1-b999-53c93193a1cb.

## Metadata

- **Maintainer** `Katrin Becker`
- **Maintainer_email** `Katrin.Becker@ba-fk.verwalt-berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2015-11-09`
- **Metadata_created** `2016-02-18T20:39:25.763367`
- **Metadata_modified** `2016-09-30T12:25:41.388519`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 0724dd59-0d86-43b1-b999-53c93193a1cb

df <- read.csv('http://www.berlin.de/ba-friedrichshain-kreuzberg/aktuelles/fluechtlingshilfe/angebote-des-bezirksamts/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Katrin Becker | Katrin.Becker@ba-fk.verwalt-berlin.de
