---
title: "{{ DOCUMENT_TITLE }}"
date: "{{ TODAY_DATE }}"
output: html_document
---

## Dataset: Aktenplan der Senatsverwaltung für Finanzen

Aktenplan der Senatsverwaltung für Finanzen

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenfinanzenueberunsleitungorganisationaktenplan)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/finanzen/ueber-uns/leitung-organisation/aktenplan/)

Auto generated R starter code for data set 15818148-81ef-47bf-8d8b-a69617730474.

## Metadata

- **Maintainer** `Seda Hommens`
- **Maintainer_email** `seda.hommens@senfin.berlin.de`
- **Tags** `['aktenplannummer', 'aktentitel', 'aufbewahrungsfrist', 'simplesearch', 'teilaktenplan']`
- **Date_released** `2018-01-30`
- **Metadata_created** `2018-01-30T14:38:28.739548`
- **Metadata_modified** `2024-08-07T20:30:54.947817`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 15818148-81ef-47bf-8d8b-a69617730474

df <- read.csv('https://www.berlin.de/sen/finanzen/ueber-uns/leitung-organisation/aktenplan/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Seda Hommens | seda.hommens@senfin.berlin.de
