---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-17"
output: html_document
---

## Dataset: Gründungen

Gründungen

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschaftwirtschaftkonjunkturundstatistikwirtschaftsdatengruendungenod)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/wirtschaft/wirtschaft/konjunktur-und-statistik/wirtschaftsdaten/gruendungen/od/)

Auto generated R starter code for data set 1c27227d-3f61-4591-85a8-3c690506af9a.

## Metadata

- **Maintainer** `Ralf Eberhardt`
- **Maintainer_email** `ralf.eberhardt@senweb.berlin.de`
- **Tags** `['gründungen', 'insolvenzen', 'simplesearch']`
- **Date_released** `2015-02-02`
- **Metadata_created** `2017-01-09T13:09:10.520228`
- **Metadata_modified** `2019-08-16T12:29:44.267831`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 1c27227d-3f61-4591-85a8-3c690506af9a

df <- read.csv('http://www.berlin.de/sen/wirtschaft/wirtschaft/konjunktur-und-statistik/wirtschaftsdaten/gruendungen/od/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Ralf Eberhardt | ralf.eberhardt@senweb.berlin.de
