---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-28"
output: html_document
---

## Dataset: Berliner und Brandenburger Wochen- und Trödelmärkte

Wochen- und Trödelmärkte Berlin und Brandenburg

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwebservicemaerktefestewochentroedelmaerkte)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/web/service/maerkte-feste/wochen-troedelmaerkte/)

Auto generated R starter code for data set 23f72b21-d8e0-460a-b043-1b34db40d27f.

## Metadata

- **Maintainer** `Berlin.de`
- **Maintainer_email** `Abdulkadir.Dagci@senweb.berlin.de`
- **Tags** `['antikmärkte', 'simplesearch', 'trödelmärkte', 'wochenmärkte']`
- **Date_released** `2014-04-15`
- **Metadata_created** `2017-10-24T09:23:24.669824`
- **Metadata_modified** `2024-10-14T14:47:00.816813`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 23f72b21-d8e0-460a-b043-1b34db40d27f

df <- read.csv('https://www.berlin.de/sen/web/service/maerkte-feste/wochen-troedelmaerkte/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Berlin.de | Abdulkadir.Dagci@senweb.berlin.de
