---
title: "Open Government Data, Berlin Open Data"
date: "2025-01-05"
output: html_document
---

## Dataset: Straßenverzeichnis der Stadtplanung im Bezirk Lichtenberg

Dieses Straßenverzeichnis vom Bezirk Lichtenberg hilft Ihnen dabei den richtigen Ansprechpartner im Stadtentwicklungsamt Fachbereich Stadtplanung zu finden.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebalichtenbergaufeinenblickbuergerservicestadtplanung)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-lichtenberg/auf-einen-blick/buergerservice/stadtplanung/)

Auto generated R starter code for data set 2510f49a-410b-451b-a81c-d8239f6ec70c.

## Metadata

- **Maintainer** `Regina Lange`
- **Maintainer_email** `regina.lange@lichtenberg.berlin.de`
- **Tags** `['bauen', 'bebauung', 'bebauungspläne', 'bezirk', 'entwurf', 'karte', 'lichtenberg', 'plan', 'simplesearch', 'stadtentwicklung']`
- **Date_released** `2015-03-17`
- **Metadata_created** `2016-02-18T21:13:12.152389`
- **Metadata_modified** `2024-08-07T15:49:35.094599`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 2510f49a-410b-451b-a81c-d8239f6ec70c

df <- read.csv('https://www.berlin.de/ba-lichtenberg/auf-einen-blick/buergerservice/stadtplanung/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Regina Lange | regina.lange@lichtenberg.berlin.de
