---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-05"
output: html_document
---

## Dataset: BSR Entsorgungsbilanz 2007-2012

Daten der BSR-Entsorgungsbilanz 2007 bis 2012.
Enthalten sind:

* Übersicht der Siedlungsabfälle nach Fraktion
* Übersicht der Annahmemengen auf BSR Recyclinghöfen nach Abfallart
* Übersicht des Siedlungsabfallaufkommens

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=bsr-entsorgungsbilanz-2007-2012)<br>
[Direct link by BSR - Berliner Stadtreinigungsbetriebe for dataset]()

Auto generated R starter code for data set 2623963b-cc40-4450-8005-e3317fba0428.

## Metadata

- **Maintainer** `Jan Holthusen`
- **Maintainer_email** `Jan.Holthusen@BSR.de`
- **Tags** `['Entsorgung BSR Recycling']`
- **Date_released** `2013-09-05`
- **Metadata_created** `2016-02-18T21:15:33.697859`
- **Metadata_modified** `2022-03-04T15:27:02.934959`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 2623963b-cc40-4450-8005-e3317fba0428

df <- read.csv('http://www.bsr.de/opendata/entsorgungsbilanz/fraktionen_aufkommen/fraktionen.csv')

# Distribution 1
# Package_id               : 2623963b-cc40-4450-8005-e3317fba0428

df <- read.csv('http://www.bsr.de/opendata/entsorgungsbilanz/recyclinghof_annahme/rc_annahmen.csv')

# Distribution 2
# Package_id               : 2623963b-cc40-4450-8005-e3317fba0428

df <- read.csv('http://www.bsr.de/opendata/entsorgungsbilanz/siedlungsabfallaufkommen/siedlungsabfall.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Jan Holthusen | Jan.Holthusen@BSR.de
