---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-17"
output: html_document
---

## Dataset: Angebote für Neugeborene, Säuglinge und Kleinkinder

“Willkommen im Leben” Angebote für Eltern mit Ihren Kindern in Marzahn-Hellersdorf

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindewillkommenimlebenmhdieerstenjahre)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/willkommen-im-leben-mh/die-ersten-jahre/)

Auto generated R starter code for data set 2ad89e9a-a754-4536-82fe-46eb05faa72b.

## Metadata

- **Maintainer** `Angelika Herda`
- **Maintainer_email** `angelika.herda@ba-mh.berlin.de`
- **Tags** `['angebote_für_eltern_mit_ihren_kindern_in_marzahn-hellersdorf', 'simplesearch']`
- **Date_released** `2017-03-20`
- **Metadata_created** `2020-05-07T13:22:47.797368`
- **Metadata_modified** `2023-09-14T16:31:06.803760`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 2ad89e9a-a754-4536-82fe-46eb05faa72b

df <- read.csv('https://www.berlin.de/willkommen-im-leben-mh/die-ersten-jahre/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Angelika Herda | angelika.herda@ba-mh.berlin.de
