---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-12"
output: html_document
---

## Dataset: Beteiligungsdatenbank des Landes Berlin

Wirtschaftsdaten und Organdaten der Beteiligungsunternehmen des Landes Berlin

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenfinanzenvermoegenbeteiligungenbeteiligungsdatenbank)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/finanzen/vermoegen/beteiligungen/beteiligungsdatenbank/)

Auto generated R starter code for data set 2c353e09-d92c-4485-8096-d1a16bceff37.

## Metadata

- **Maintainer** `Stefan Kostka`
- **Maintainer_email** `stefan.kostka@senfin.berlin.de`
- **Tags** `['beiteiligungen', 'beteiligungsunternehmen', 'simplesearch']`
- **Date_released** `2014-01-09`
- **Metadata_created** `2019-11-20T11:27:30.109742`
- **Metadata_modified** `2024-11-01T13:14:45.939223`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 2c353e09-d92c-4485-8096-d1a16bceff37

df <- read.csv('https://www.berlin.de/sen/finanzen/vermoegen/beteiligungen/beteiligungsdatenbank/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Stefan Kostka | stefan.kostka@senfin.berlin.de
