---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-01"
output: html_document
---

## Dataset: Welcher Regionale Soziale Dienst ist für Sie zuständig? (Straßenverzeichnis)

Zuordnung von Straßen und Hausnummern zu den Regionalen Diensten des Jugendamtes Steglitz-Zehlendorf

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebasteglitzzehlendorfpolitikundverwaltungaemterjugendamtsimplesearch)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-steglitz-zehlendorf/politik-und-verwaltung/aemter/jugendamt/simple-search/)

Auto generated R starter code for data set 2f13f7c1-71a3-4631-976e-95fb2e6ba5c0.

## Metadata

- **Maintainer** `Lutz Meinert`
- **Maintainer_email** `jugendamt-it@ba-sz.berlin.de`
- **Tags** `['regionale_dienste', 'simplesearch', 'straßenverzeichnis']`
- **Date_released** `2014-06-17`
- **Metadata_created** `2016-02-18T21:02:39.698303`
- **Metadata_modified** `2024-08-07T16:14:23.451228`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 2f13f7c1-71a3-4631-976e-95fb2e6ba5c0

df <- read.csv('https://www.berlin.de/ba-steglitz-zehlendorf/politik-und-verwaltung/aemter/jugendamt/simple-search/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Lutz Meinert | jugendamt-it@ba-sz.berlin.de
