---
title: "{{ DOCUMENT_TITLE }}"
date: "{{ TODAY_DATE }}"
output: html_document
---

## Dataset: Kindertagesstätten in Marzahn-Hellersdorf

Kindertagesstätten in Marzahn-Hellersdorf

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebamarzahnheller_ff09f1e65b4654d0f2b50ea38eba6963_gundbildungkitasuche)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/betreuung-und-bildung/kitasuche/)

Auto generated R starter code for data set 3180cdf2-7495-4880-8460-c879db1418a6.

## Metadata

- **Maintainer** `Angelika Herda`
- **Maintainer_email** `angelika.herda@ba-mh.berlin.de`
- **Tags** `['kindertagesstätten_in_marzahn-hellersdorf', 'nach_regionen_sortiert', 'simplesearch']`
- **Date_released** `2014-12-29`
- **Metadata_created** `2016-02-18T20:30:06.742929`
- **Metadata_modified** `2024-08-07T15:55:38.049254`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 3180cdf2-7495-4880-8460-c879db1418a6

df <- read.csv('https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/betreuung-und-bildung/kitasuche/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Angelika Herda | angelika.herda@ba-mh.berlin.de
