---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-16"
output: html_document
---

## Dataset: Senatsvorlagen der Senatsverwaltung für Wirtschaft, Energie und Betriebe

Parlamentsdokumentation

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschaftserviceparlamentsdokumentation)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/wirtschaft/service/parlamentsdokumentation/)

Auto generated R starter code for data set 32a15add-28a6-49af-9dc3-a8cff85c2ed0.

## Metadata

- **Maintainer** `Ralf Eberhardt`
- **Maintainer_email** `ralf.eberhardt@senweb.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2016-04-27`
- **Metadata_created** `2016-04-28T09:52:48.528194`
- **Metadata_modified** `2017-08-21T11:50:35.205781`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 32a15add-28a6-49af-9dc3-a8cff85c2ed0

df <- read.csv('http://www.berlin.de/sen/wirtschaft/service/parlamentsdokumentation/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Ralf Eberhardt | ralf.eberhardt@senweb.berlin.de
