---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-22"
output: html_document
---

## Dataset: Doppelhaushalt 2022/2023 (2.Nachtrag)

Der Haushaltsplan bietet einen Überblick über die geplanten Ausgaben und Einnahmen des Landes Berlin.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=doppelhaushalt-2022-2023-2-nachtrag-1464527)<br>
[Direct link by Datenrubrik for dataset]()

Auto generated R starter code for data set 32f7c2b3-6c39-41b6-b534-74759c4bb890.

## Metadata

- **Maintainer** `Julia Schabos`
- **Maintainer_email** `julia.schabos@senfin.berlin.de`
- **Tags** `['Haushaltsplan', 'Landeshaushalt']`
- **Date_released** `2024-07-09`
- **Metadata_created** `2024-07-10T07:01:13.487616`
- **Metadata_modified** `2024-07-10T07:03:03.558980`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 32f7c2b3-6c39-41b6-b534-74759c4bb890

df <- read.csv('https://www.berlin.de/sen/finanzen/service/daten/doppelhaushalt_22_23_nachtrag.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Julia Schabos | julia.schabos@senfin.berlin.de
