---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-19"
output: html_document
---

## Dataset: Branchenübersicht

Die Übersicht enthält wesentliche im Gemeinsamen Tarifregister Berlin und Brandenburg vorliegende und in der Region geltende tarifvertraglich geregelte Ausbildungsvergütungen.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenarbeitberlin_6e0d5bb6e966f32a7dcb2c642bb17533_enbranchenuebersicht)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/arbeit/berlinarbeit-ziel-2/tarifregister/tarif-informationen/ausbildungsverguetungen/branchenuebersicht/)

Auto generated R starter code for data set 36edd704-d220-495d-b459-59fab54715b6.

## Metadata

- **Maintainer** `Anette Leiner`
- **Maintainer_email** `tarifregister@senias.berlin.de`
- **Tags** `['simplesearch', 'tarifregister_tarifauskunft_tarifvertrag_ausbildungsvergütungen_branchen_berlin_brandenburg']`
- **Date_released** `2016-05-24`
- **Metadata_created** `2016-09-20T20:18:41.293734`
- **Metadata_modified** `2018-07-13T12:30:26.823221`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 36edd704-d220-495d-b459-59fab54715b6

df <- read.csv('http://www.berlin.de/sen/arbeit/berlinarbeit-ziel-2/tarifregister/tarif-informationen/ausbildungsverguetungen/branchenuebersicht/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Anette Leiner | tarifregister@senias.berlin.de
