---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-19"
output: html_document
---

## Dataset: Tourismus in Berlin 2016

Berlin-Tourismus 2016

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschaftwirtschaftbranchentourismustourismusinzahlen4od1)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/wirtschaft/wirtschaft/branchen/tourismus/tourismus-in-zahlen/4od1/)

Auto generated R starter code for data set 386b1bdf-431d-4723-9f36-39f03a7a5ade.

## Metadata

- **Maintainer** `Ralf Eberhardt`
- **Maintainer_email** `ralf.eberhardt@senweb.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2017-06-30`
- **Metadata_created** `2017-06-30T13:32:36.554687`
- **Metadata_modified** `2019-08-18T15:03:29.157050`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 386b1bdf-431d-4723-9f36-39f03a7a5ade

df <- read.csv('http://www.berlin.de/sen/wirtschaft/wirtschaft/branchen/tourismus/tourismus-in-zahlen/4od1/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Ralf Eberhardt | ralf.eberhardt@senweb.berlin.de
