---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-01"
output: html_document
---

## Dataset: Einwohnerinnen und Einwohner in Berlin in LOR-Planungsräumen am 31.12.2011

Einwohnerinnen und Einwohner in Berlin in LOR-Planungsräumen am 31.12.2011

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=einwohnerinnen-und-einwohner-in-berlin-in-lor-planungsr-umen-am-31-12-2011)<br>
[Direct link by Amt für Statistik Berlin-Brandenburg for dataset](https://www.statistik-berlin-brandenburg.de)

Auto generated R starter code for data set 3adcfb87-c5e5-4cb7-9f69-918dce763dad.

## Metadata

- **Maintainer** `Amt für Statistik Berlin-Brandenburg`
- **Maintainer_email** `einwohner@statistik-bbb.de`
- **Tags** `['Einwohner', 'kleinräumige Einwohnerzahl']`
- **Date_released** `2013-06-17`
- **Metadata_created** `2016-02-18T20:27:28.715724`
- **Metadata_modified** `2019-05-13T11:32:56.518036`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 3adcfb87-c5e5-4cb7-9f69-918dce763dad

df <- read.csv('https://www.statistik-berlin-brandenburg.de/opendata/EWR201112E_Matrix.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Amt für Statistik Berlin-Brandenburg | einwohner@statistik-bbb.de
