---
title: "Open Government Data, Berlin Open Data"
date: "2025-02-02"
output: html_document
---

## Dataset: Übersicht über mögliche Tarifentgelte – Ausgewählte Berufe

Übersicht über mögliche Tarifentgelte für die Berufe Bürokauffrau/-mann mit Berufsabschluss und Kraftfahrer in Berlin und Brandenburg.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenarbeitberlin_ab4ac9a51957e726e381a7b3977b4cc3_enausgewaehlteberufe)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/arbeit/berlinarbeit-ziel-2/tarifregister/tarif-informationen/ausgewaehlte-berufe/)

Auto generated R starter code for data set 3ae4b1fa-e2bd-47e1-81b6-178a572e5ca1.

## Metadata

- **Maintainer** `Anette Leiner`
- **Maintainer_email** `tarifregister@senias.berlin.de`
- **Tags** `['berlin', 'branche', 'brandenburg', 'bürokauffrau', 'bürokaufmann', 'kraftfahrer', 'simplesearch', 'tarifauskunft', 'tarifentgelt', 'tarifregister']`
- **Date_released** `2016-10-20`
- **Metadata_created** `2016-11-25T11:35:12.570887`
- **Metadata_modified** `2018-07-19T14:13:43.560057`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 3ae4b1fa-e2bd-47e1-81b6-178a572e5ca1

df <- read.csv('http://www.berlin.de/sen/arbeit/berlinarbeit-ziel-2/tarifregister/tarif-informationen/ausgewaehlte-berufe/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Anette Leiner | tarifregister@senias.berlin.de
