---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-25"
output: html_document
---

## Dataset: Zuwendungsdatenbank

Haushalt, Zuwendungen, Zuwendungsempfänger

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenfinanzenservicezuwendungsdatenbank)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/finanzen/service/zuwendungsdatenbank/)

Auto generated R starter code for data set 3d10a166-d490-4ab9-9815-e604d41c46a3.

## Metadata

- **Maintainer** `Jean Winkler-Schneider`
- **Maintainer_email** `Jean.Winkler-Schneider@senfin.berlin.de`
- **Tags** `['haushalt', 'simplesearch', 'zuwendungen', 'zuwendungsempfänger']`
- **Date_released** `2013-02-05`
- **Metadata_created** `2016-02-18T20:50:47.674559`
- **Metadata_modified** `2024-10-24T07:31:01.553069`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 3d10a166-d490-4ab9-9815-e604d41c46a3

df <- read.csv('https://www.berlin.de/sen/finanzen/service/zuwendungsdatenbank/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Jean Winkler-Schneider | Jean.Winkler-Schneider@senfin.berlin.de
