---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-04"
output: html_document
---

## Dataset: Denkmalliste des Landes Berlin

Die Denkmalliste des Landes Berlin enthält mehr als 12.000 Objekte. Sie ist gruppiert nach Stadtbezirken und Denkmalbereichen.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=denkmalliste-des-landes-berlin)<br>
[Direct link by Landesdenkmalamt for dataset](http://www.berlin.de/landesdenkmalamt/denkmale/liste-karte-datenbank/denkmalliste/)

Auto generated R starter code for data set 3d2fefc5-384a-4c1c-b55b-b55cfb34d321.

## Metadata

- **Maintainer** `Juliane Stamm`
- **Maintainer_email** `juliane.stamm@lda.berlin.de`
- **Tags** `['denkmal']`
- **Date_released** `2012-02-28`
- **Metadata_created** `2016-02-18T20:47:57.545833`
- **Metadata_modified** `2023-12-07T10:54:09.683807`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 3d2fefc5-384a-4c1c-b55b-b55cfb34d321

df <- read.csv('https://www.berlin.de/landesdenkmalamt/_assets/pdf-und-zip/denkmale/liste-karte-datenbank/denkmalliste_berlin.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Juliane Stamm | juliane.stamm@lda.berlin.de
