---
title: "Open Government Data, Berlin Open Data"
date: "2025-01-19"
output: html_document
---

## Dataset: Angebote für jedes Alter



    Angebote für Kinder, Jugend und Familie
  


[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebamarzahnheller_a23d706a920c6370740922b93687e625_ungundunterstuetzung)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/beratung-und-unterstuetzung/)

Auto generated R starter code for data set 4a65ae43-33e8-4339-922a-bf00363f86eb.

## Metadata

- **Maintainer** `Angelika Herda`
- **Maintainer_email** `angelika.herda@ba-mh.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2015-02-26`
- **Metadata_created** `2016-02-18T21:24:53.831283`
- **Metadata_modified** `2016-02-18T21:24:53.850519`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 4a65ae43-33e8-4339-922a-bf00363f86eb

df <- read.csv('http://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/beratung-und-unterstuetzung/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Angelika Herda | angelika.herda@ba-mh.berlin.de
