---
title: "Open Government Data, Berlin Open Data"
date: "2024-12-09"
output: html_document
---

## Dataset: Bruttoinlandsprodukt

BIP 2011 - 2016

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschaftwi_345c2d0884a44cbcde58d35aaa9c885d_bruttoinlandsprodukt)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/wirtschaft/wirtschaft/konjunktur-und-statistik/wirtschaftsdaten/wirtschaftsleistung/bruttoinlandsprodukt/)

Auto generated R starter code for data set 530f39e6-e4eb-4432-9e3a-57a8b7bac8ac.

## Metadata

- **Maintainer** `Ralf Eberhardt`
- **Maintainer_email** `ralf.eberhardt@senweb.berlin.de`
- **Tags** `['bruttoinlandsprodukt', 'ii633502', 'simplesearch']`
- **Date_released** `2017-09-22`
- **Metadata_created** `2017-09-22T14:17:58.322283`
- **Metadata_modified** `2018-01-29T09:26:41.602018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 530f39e6-e4eb-4432-9e3a-57a8b7bac8ac

df <- read.csv('http://www.berlin.de/sen/wirtschaft/wirtschaft/konjunktur-und-statistik/wirtschaftsdaten/wirtschaftsleistung/bruttoinlandsprodukt/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Ralf Eberhardt | ralf.eberhardt@senweb.berlin.de
