---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-27"
output: html_document
---

## Dataset: Sportangebote in Marzahn-Hellersdorf

Sportstätten im Bezirk Marzahn-Hellersdorf

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebamarzahnheller_cd9227901bfb29a8fad81648bd4477a7_inmarzahnhellersdorf)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/schul-und-sportamt/sportangebote-in-marzahn-hellersdorf/)

Auto generated R starter code for data set 5382721e-01c6-47b2-8013-e40330970d19.

## Metadata

- **Maintainer** `Berlin.de`
- **Maintainer_email** `uta.simdorn@ba-mh.berlin.de`
- **Tags** `['senatskanzlei', 'simplesearch', 'sport', 'sportangebote', 'sportplätze']`
- **Date_released** `2013-08-27`
- **Metadata_created** `2023-09-14T16:26:05.297617`
- **Metadata_modified** `2023-09-14T16:26:05.297624`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5382721e-01c6-47b2-8013-e40330970d19

df <- read.csv('https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/schul-und-sportamt/sportangebote-in-marzahn-hellersdorf/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Berlin.de | uta.simdorn@ba-mh.berlin.de
