---
title: "Open Government Data, Berlin Open Data"
date: "2025-01-19"
output: html_document
---

## Dataset: Öffentliche Toiletten im Bezirk Lichtenberg

Öffentlich zugängliche Toiletten Im Bezirk Lichtenberg.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebalichtenbergaufeinenblickwirtschafttoiletten)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-lichtenberg/auf-einen-blick/wirtschaft/toiletten/)

Auto generated R starter code for data set 5bce5dc6-e71e-4609-ac66-b0c8576af3f6.

## Metadata

- **Maintainer** `Büttner`
- **Maintainer_email** `christian.buettner@lichtenberg.berlin.de`
- **Tags** `['berlin', 'clo', 'lichtenberg_öffentliche_toiletten', 'simplesearch', 'stilles_örtchen', 'toilets', 'toiletten', 'wc', 'öffentliches_wc']`
- **Date_released** `2015-06-25`
- **Metadata_created** `2016-02-18T21:11:10.157482`
- **Metadata_modified** `2024-08-07T15:49:57.237314`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5bce5dc6-e71e-4609-ac66-b0c8576af3f6

df <- read.csv('https://www.berlin.de/ba-lichtenberg/auf-einen-blick/wirtschaft/toiletten/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Büttner | christian.buettner@lichtenberg.berlin.de
