---
title: "Open Government Data, Berlin Open Data"
date: "2024-12-29"
output: html_document
---

## Dataset: Stadtführer Entwicklungspolitik

Stadtführer Entwicklungspolitik

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschafteu_d8dd7a2bd51e79fea1967afc40433c89_rentwicklungspolitik)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/wirtschaft/europa-und-internationales/landesstelle-fuer-entwicklungszusammenarbeit/stadtfuehrer-entwicklungspolitik/)

Auto generated R starter code for data set 5cda6b75-5625-4ada-9899-351f3c0d325d.

## Metadata

- **Maintainer** `Ralf Eberhardt`
- **Maintainer_email** `ralf.eberhardt@senweb.berlin.de`
- **Tags** `['entwicklungspolitik', 'simplesearch']`
- **Date_released** `2014-07-29`
- **Metadata_created** `2022-02-05T05:06:30.229753`
- **Metadata_modified** `2024-08-07T20:11:48.862166`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5cda6b75-5625-4ada-9899-351f3c0d325d

df <- read.csv('https://www.berlin.de/sen/wirtschaft/europa-und-internationales/landesstelle-fuer-entwicklungszusammenarbeit/stadtfuehrer-entwicklungspolitik/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Ralf Eberhardt | ralf.eberhardt@senweb.berlin.de
