---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-25"
output: html_document
---

## Dataset: Förderungen / Finanzen

Sammlung von Fördermöglichkeiten

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebatreptowkoepen_4ec2462f9453e8a8fc6f9bcdbb206e4d_finanzensimplesearch)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-treptow-koepenick/politik-und-verwaltung/beauftragte/integration/foerderungen-finanzen/simplesearch/)

Auto generated R starter code for data set 6587221b-3e5d-49a7-8563-783984da71f5.

## Metadata

- **Maintainer** `Katharina Stökl`
- **Maintainer_email** `katharina.stoekl@ba-tk.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2019-03-22`
- **Metadata_created** `2019-03-22T08:42:09.537707`
- **Metadata_modified** `2024-08-07T16:20:39.436178`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 6587221b-3e5d-49a7-8563-783984da71f5

df <- read.csv('https://www.berlin.de/ba-treptow-koepenick/politik-und-verwaltung/beauftragte/integration/foerderungen-finanzen/simplesearch/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Katharina Stökl | katharina.stoekl@ba-tk.berlin.de
