---
title: "Open Government Data, Berlin Open Data"
date: "2024-12-15"
output: html_document
---

## Dataset: Europawahl 2019 in Berlin nach Wahlbezirken (Endgültiges Ergebnis)

Europawahl 2019 in Berlin nach Wahlbezirken (Endgültiges Ergebnis)

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=europawahl-2019-in-berlin-nach-wahlbezirken-endgultiges-ergebnis)<br>
[Direct link by Amt für Statistik Berlin-Brandenburg for dataset](https://www.statistik-berlin-brandenburg.de)

Auto generated R starter code for data set 65bc133e-14f0-4a02-924e-8b491591f6db.

## Metadata

- **Maintainer** ``
- **Maintainer_email** `wahlstatistik@statistik-bbb.de`
- **Tags** `['2019', 'Berlin', 'Briefwähler', 'Europawahl', 'Stimmbezirke', 'Urnenwähler', 'Wahlbezirke', 'Wähler']`
- **Date_released** `2019-09-12`
- **Metadata_created** `2019-09-12T07:56:41.887611`
- **Metadata_modified** `2020-10-12T14:25:21.823681`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 65bc133e-14f0-4a02-924e-8b491591f6db

df <- read.csv('https://www.statistik-berlin-brandenburg.de/opendata/EU2019_BE_EndgErg_Wahlbezirke.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

No contact information provided.
