---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-01"
output: html_document
---

## Dataset: Angebote für 'KINDER, JUGEND und FAMILIE'

Angebote für Kinder, Jugend und Familie

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebamarzahnheller_276a28646148d03ceee6a99ea6ee11de_stuetzungangeboteneu)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/beratung-und-unterstuetzung/angeboteneu/)

Auto generated R starter code for data set 66ede38a-829c-4494-907b-cf7bd8cc72bf.

## Metadata

- **Maintainer** `Angelika Herda`
- **Maintainer_email** `angelika.herda@ba-mh.berlin.de`
- **Tags** `['angebote_für_kinder', 'jugend_und_familie', 'simplesearch']`
- **Date_released** `2015-02-26`
- **Metadata_created** `2016-02-18T20:17:39.754284`
- **Metadata_modified** `2024-08-07T15:54:50.624033`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 66ede38a-829c-4494-907b-cf7bd8cc72bf

df <- read.csv('https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/beratung-und-unterstuetzung/angeboteneu/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Angelika Herda | angelika.herda@ba-mh.berlin.de
