---
title: "Open Government Data, Berlin Open Data"
date: "2024-12-29"
output: html_document
---

## Dataset: Orte für 'KINDER, JUGEND und FAMILIE'

Orte für “KINDER, JUGEND und FAMILIE”

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebamarzahnhellersdorfpolitikundverwaltungaemterjugendamteinrichtungssuche)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/einrichtungssuche/)

Auto generated R starter code for data set 6877650b-6f74-4e0d-aed2-f3fe1bcc07a7.

## Metadata

- **Maintainer** `Viktoria Funk`
- **Maintainer_email** `viktoria.funk@ba-mh.berlin.de`
- **Tags** `['familie', 'jugend', 'kinder', 'simplesearch']`
- **Date_released** `2014-12-29`
- **Metadata_created** `2016-02-18T20:44:25.989573`
- **Metadata_modified** `2024-11-21T10:06:13.487804`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 6877650b-6f74-4e0d-aed2-f3fe1bcc07a7

df <- read.csv('https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/einrichtungssuche/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Viktoria Funk | viktoria.funk@ba-mh.berlin.de
