---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-16"
output: html_document
---

## Dataset: Meldeportal nicht zertifizierungspflichtiger Lebensmitteleinzelhändler

Behördliche Überwachung im Bereich EU-Öko-Kontrollen, hier: Daten nicht zertifizierungspflichtiger Lebensmitteleinzelhändler.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindelagesogesundheitoekokontrollemeldeportalble)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/lageso/gesundheit/oekokontrolle/meldeportal-ble/)

Auto generated R starter code for data set 6d4b38d9-7929-44e8-8361-a8c8ff27bb75.

## Metadata

- **Maintainer** `Herr Scholz`
- **Maintainer_email** `oekokontrolle@lageso.berlin.de`
- **Tags** `['eu-verordnungen', 'eu-öko-kontrollen', 'simplesearch', 'überwachung']`
- **Date_released** `2015-07-22`
- **Metadata_created** `2024-11-06T16:17:02.370596`
- **Metadata_modified** `2024-11-06T16:36:59.158239`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 6d4b38d9-7929-44e8-8361-a8c8ff27bb75

df <- read.csv('https://www.berlin.de/lageso/gesundheit/oekokontrolle/meldeportal-ble/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Herr Scholz | oekokontrolle@lageso.berlin.de
