---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-15"
output: html_document
---

## Dataset: Kamerale Monatsdaten Bezirk Marzahn-Hellersdorf 2015

Stand der Haushaltswirtschaft des Bezirkes Marzahn-Hellersdorf zum jeweiligen Monatsende je Kapitel und Titel.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=kamerale-monatsdaten-bezirk-marzahn-hellersdorf-2015)<br>
[Direct link by Bezirksamt Marzahn-Hellersdorf for dataset](http://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/service-und-organisationseinheiten/finanzen/)

Auto generated R starter code for data set 71f010a1-119d-496c-b783-dc1bfbf36310.

## Metadata

- **Maintainer** ``
- **Maintainer_email** `ilona.lutzke@ba-mh.verwalt-berlin.de`
- **Tags** `['Kamerale Monatsdaten Bezirk Marzahn-Hellersdorf 2015']`
- **Date_released** `2015-03-19`
- **Metadata_created** `2016-02-18T20:21:13.928480`
- **Metadata_modified** `2016-11-17T11:36:34.237792`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 71f010a1-119d-496c-b783-dc1bfbf36310

df <- read.csv('https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/service-und-organisationseinheiten/finanzen/kamerale-monatsdaten/kopie-von-kamerale_monatsdaten_10_2015.csv')

# Distribution 1
# Package_id               : 71f010a1-119d-496c-b783-dc1bfbf36310

df <- read.csv('https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/service-und-organisationseinheiten/finanzen/kamerale-monatsdaten/kamerale_monatsdaten_11_2015.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

No contact information provided.
