---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-17"
output: html_document
---

## Dataset: Strassenverkehrsunfälle nach Unfallort in Berlin 2020

Strassenverkehrsunfälle nach Unfallort mit Strassenname, GPS-Koordinaten und  LOR-Planungsraum in Berlin 2020; Unfallmonat, -wochentag, - stunde; Unfallart und -kategorie

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=strassenverkehrsunfalle-nach-unfallort-in-berlin-2020)<br>
[Direct link by Amt für Statistik Berlin-Brandenburg for dataset](https://www.statistik-berlin-brandenburg.de/)

Auto generated R starter code for data set 73662880-7293-447e-8a1a-5eedac6f9856.

## Metadata

- **Maintainer** ``
- **Maintainer_email** `verkehr@statistik-bbb.de`
- **Tags** `['2020', 'Berlin', 'Koordinaten', 'LOR Planungsräume', 'Strassenverkehrsunfälle', 'Unfallart', 'Unfallkategorie', 'Unfallmonat', 'Unfallstunde', 'Unfallwochentag', 'Unfälle']`
- **Date_released** `2021-08-13`
- **Metadata_created** `2021-08-06T10:42:04.938388`
- **Metadata_modified** `2021-08-13T07:58:56.837418`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 73662880-7293-447e-8a1a-5eedac6f9856

df <- read.csv('https://www.statistik-berlin-brandenburg.de/opendata/AfSBBB_BE_LOR_Strasse_Strassenverkehrsunfaelle_2020_Datensatz.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

No contact information provided.
