---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-03"
output: html_document
---

## Dataset: Angebote der schulbezogenen Jugendarbeit und Jugendsozialarbeit

Übersicht der Angebote der schulbezogenen Jugendarbeit und Jugendsozialarbeit im Bezirk Lichtenberg

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebalichtenbergaufeinenblickfreizeitsportjajsa)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-lichtenberg/auf-einen-blick/freizeit/sport/ja-jsa/)

Auto generated R starter code for data set 749f56ff-4c53-4d98-b53c-3af79ce39002.

## Metadata

- **Maintainer** `Kerstin Nieber`
- **Maintainer_email** `kerstin.nieber@lichtenberg.berlin.de`
- **Tags** `['angebote', 'integrierte_sekundarschulen', 'projekte', 'schulen_mit_sonderpädagogischem_förderschwerpunkt', 'schulsozialarbeit', 'schulstationen', 'schülerclubs_an_grundschulen', 'simplesearch']`
- **Date_released** `2015-07-13`
- **Metadata_created** `2016-02-18T21:25:27.315638`
- **Metadata_modified** `2024-08-07T15:49:21.680529`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 749f56ff-4c53-4d98-b53c-3af79ce39002

df <- read.csv('https://www.berlin.de/ba-lichtenberg/auf-einen-blick/freizeit/sport/ja-jsa/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Kerstin Nieber | kerstin.nieber@lichtenberg.berlin.de
