---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-10"
output: html_document
---

## Dataset: Passendes OSZ finden

Liste der Oberstufenzentren (OSZ) in Berlin mit Bildungsgängen und Berufsfeldern.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindeoszoszkarte)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/osz/osz-karte/)

Auto generated R starter code for data set 76919e2d-eb5a-451f-a96b-d677181d5a77.

## Metadata

- **Maintainer** `Karen König`
- **Maintainer_email** `open-data@senbjf.berlin.de`
- **Tags** `['berufsschule', 'oberstufenzentrum', 'osz', 'simplesearch']`
- **Date_released** `2023-12-04`
- **Metadata_created** `2024-02-01T14:28:30.223448`
- **Metadata_modified** `2024-08-07T18:39:47.507822`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 76919e2d-eb5a-451f-a96b-d677181d5a77

df <- read.csv('https://www.berlin.de/osz/osz-karte/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Karen König | open-data@senbjf.berlin.de
