---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-13"
output: html_document
---

## Dataset: Angebote für Flüchtlinge im Bezirk

Angebote von Trägern zur Unterstützung von Flüchtlingen im Bezirk Friedrichshain-Kreuzberg

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebafriedrichshai_130a12879f6c4007066388b6831fb2ad_zirktraegerundaemter)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/ba-friedrichshain-kreuzberg/aktuelles/fluechtlingshilfe/angebote-im-bezirk/traeger-und-aemter/)

Auto generated R starter code for data set 7a2e6767-2aed-4f45-9848-a828f2871b7e.

## Metadata

- **Maintainer** `Katrin Becker`
- **Maintainer_email** `Katrin.Becker@ba-fk.verwalt-berlin.de`
- **Tags** `['angebote', 'flüchtlinge', 'flüchtlingshilfe', 'hilfe', 'refugees', 'simplesearch', 'unterstützung']`
- **Date_released** `2015-10-12`
- **Metadata_created** `2017-01-30T10:41:05.643949`
- **Metadata_modified** `2019-08-19T13:21:18.334790`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 7a2e6767-2aed-4f45-9848-a828f2871b7e

df <- read.csv('http://www.berlin.de/ba-friedrichshain-kreuzberg/aktuelles/fluechtlingshilfe/angebote-im-bezirk/traeger-und-aemter/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Katrin Becker | Katrin.Becker@ba-fk.verwalt-berlin.de
