---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-14"
output: html_document
---

## Dataset: Ansprechpartner/innen der Vereine: Sport f체r 4 bis 16 J채hrige



    Ansprechpartner/innen der Sportvereine in
    Charlottenburg-Wilmersdorf: Sport f체r 4 bis 16 J채hrige
  


[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebacharlottenbur_43f209611a5da755e60e5685482df03b_bis16ansprechpartner)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/ba-charlottenburg-wilmersdorf/verwaltung/aemter/schul-und-sportamt/sportamt/sportvereine/sport-von-4-bis-16/ansprechpartner/)

Auto generated R starter code for data set 81188287-5f4c-45a1-bc45-844fe4dc5542.

## Metadata

- **Maintainer** `Sandra Gottschalk`
- **Maintainer_email** `Sandra.Gottschalk@charlottenburg-wilmersdorf.de`
- **Tags** `['simplesearch']`
- **Date_released** `2016-06-09`
- **Metadata_created** `2016-07-06T11:42:59.238971`
- **Metadata_modified** `2016-09-28T09:48:26.608178`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 81188287-5f4c-45a1-bc45-844fe4dc5542

df <- read.csv('http://www.berlin.de/ba-charlottenburg-wilmersdorf/verwaltung/aemter/schul-und-sportamt/sportamt/sportvereine/sport-von-4-bis-16/ansprechpartner/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Sandra Gottschalk | Sandra.Gottschalk@charlottenburg-wilmersdorf.de
