---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-30"
output: html_document
---

## Dataset: Versammlungen im Land Berlin

Versamlungen im Land Berlin

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindepolizeiserviceversammlungsbehoerdeversammlungenaufzuege)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/polizei/service/versammlungsbehoerde/versammlungen-aufzuege/)

Auto generated R starter code for data set 8422a142-d159-492e-8612-6618507769db.

## Metadata

- **Maintainer** `Polizei Berlin`
- **Maintainer_email** `onlineredaktion@polizei.berlin.de`
- **Tags** `['aufzüge', 'demonstrationen', 'demos', 'simplesearch']`
- **Date_released** `2021-03-04`
- **Metadata_created** `2021-03-19T05:28:27.811301`
- **Metadata_modified** `2024-05-21T14:57:20.984939`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 8422a142-d159-492e-8612-6618507769db

df <- read.csv('https://www.berlin.de/polizei/service/versammlungsbehoerde/versammlungen-aufzuege/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Polizei Berlin | onlineredaktion@polizei.berlin.de
