---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-07"
output: html_document
---

## Dataset: Beteiligungsdaten des Landes Berlin

Wirtschaftsdaten und Organdaten der Beteiligungsunternehmen des Landes Berlin

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=beteiligungsdaten-des-landes-berlin-1156292)<br>
[Direct link by Datenrubrik for dataset](https://www.berlin.de/sen/finanzen/vermoegen/beteiligungen/beteiligungsdatenbank/)

Auto generated R starter code for data set 89c6b31f-cbe2-4b1e-85e9-e9d0da3c853c.

## Metadata

- **Maintainer** `Stefan Kostka`
- **Maintainer_email** `stefan.kostka@senfin.berlin.de`
- **Tags** `['Beiteiligungen', 'Beteiligungsunternehmen']`
- **Date_released** `2021-06-30`
- **Metadata_created** `2021-12-10T15:27:01.739575`
- **Metadata_modified** `2021-12-10T15:32:36.268498`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 89c6b31f-cbe2-4b1e-85e9-e9d0da3c853c

df <- read.csv('https://www.berlin.de/sen/finanzen/service/daten/beteiligungsbericht.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Stefan Kostka | stefan.kostka@senfin.berlin.de
