---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-06"
output: html_document
---

## Dataset: Finanzamt-Suche

Liste der Berliner Finanzämter

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenfinanzensteuernfinanzaemterzustaendigkeitfinden)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/finanzen/steuern/finanzaemter/zustaendigkeit-finden/)

Auto generated R starter code for data set 8ff72e8d-a24e-49ae-b78c-570d1b969fa5.

## Metadata

- **Maintainer** `Berlin.de`
- **Maintainer_email** `onlineredaktion@senfin.berlin.de`
- **Tags** `['finanzamt', 'finanzverwaltung', 'finanzämter', 'simplesearch', 'steuern', 'steuerverwaltung']`
- **Date_released** `2013-02-27`
- **Metadata_created** `2016-07-25T06:58:06.356000`
- **Metadata_modified** `2021-04-01T13:09:32.144823`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 8ff72e8d-a24e-49ae-b78c-570d1b969fa5

df <- read.csv('https://www.berlin.de/sen/finanzen/steuern/finanzaemter/zustaendigkeit-finden/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Berlin.de | onlineredaktion@senfin.berlin.de
