---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-13"
output: html_document
---

## Dataset: Suche von Förderprogrammen, Projekten und Wettbewerben

Fördermöglichkeiten

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebatreptowkoepen_f01a7191b764b9f0c2b4940645f20749_tbewerbesimplesearch)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/ba-treptow-koepenick/politik-und-verwaltung/beauftragte/integration/foerderprogramme-projekte-wettbewerbe/simplesearch/)

Auto generated R starter code for data set 96a16bf8-2bd2-4c78-a178-7aa034bbeae1.

## Metadata

- **Maintainer** `Christine Herm`
- **Maintainer_email** `christine.herm@ba-tk.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2015-07-14`
- **Metadata_created** `2017-03-07T17:27:45.896430`
- **Metadata_modified** `2019-04-05T08:43:54.262026`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 96a16bf8-2bd2-4c78-a178-7aa034bbeae1

df <- read.csv('http://www.berlin.de/ba-treptow-koepenick/politik-und-verwaltung/beauftragte/integration/foerderprogramme-projekte-wettbewerbe/simplesearch/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Christine Herm | christine.herm@ba-tk.berlin.de
