---
title: "{{ DOCUMENT_TITLE }}"
date: "{{ TODAY_DATE }}"
output: html_document
---

## Dataset: Berliner Straßen- und Volksfeste 2017

Berliner Straßen- und Volksfeste 2017

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschaftservicemaerktefestestrassenvolksfeste)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/wirtschaft/service/maerkte-feste/strassen-volksfeste/)

Auto generated R starter code for data set a0c185c6-ca65-40e2-bc8a-0606a9c6de72.

## Metadata

- **Maintainer** `Ralf Eberhardt`
- **Maintainer_email** `ralf.eberhardt@senweb.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2014-04-15`
- **Metadata_created** `2016-02-18T20:52:33.971602`
- **Metadata_modified** `2017-09-18T08:37:38.524150`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a0c185c6-ca65-40e2-bc8a-0606a9c6de72

df <- read.csv('http://www.berlin.de/sen/wirtschaft/service/maerkte-feste/strassen-volksfeste/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Ralf Eberhardt | ralf.eberhardt@senweb.berlin.de
