---
title: "Open Government Data, Berlin Open Data"
date: "2024-12-09"
output: html_document
---

## Dataset: Angebote zur Unterstützung von Flüchtlingen

Angebote von Trägern zur Unterstützung von Flüchtlingen im Bezirk Friedrichshain-Kreuzberg

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebafriedrichshai_f641d27fcb5a8c99be783b90328f7cb5_tiativensimplesearch)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-friedrichshain-kreuzberg/politik-und-verwaltung/koordinatorinnen-und-koordinatoren/gefluechtete/service/angebote-und-initiativen/simplesearch/)

Auto generated R starter code for data set a0ef129e-7e16-4459-945c-f2e647ca4302.

## Metadata

- **Maintainer** `Katrin Becker`
- **Maintainer_email** `Katrin.Becker@ba-fk.verwalt-berlin.de`
- **Tags** `['angebote', 'flüchtlinge', 'flüchtlingshilfe', 'hilfe', 'refugees', 'simplesearch', 'unterstützung']`
- **Date_released** `2015-10-12`
- **Metadata_created** `2019-09-03T09:14:47.638408`
- **Metadata_modified** `2024-08-07T15:47:48.571841`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a0ef129e-7e16-4459-945c-f2e647ca4302

df <- read.csv('https://www.berlin.de/ba-friedrichshain-kreuzberg/politik-und-verwaltung/koordinatorinnen-und-koordinatoren/gefluechtete/service/angebote-und-initiativen/simplesearch/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Katrin Becker | Katrin.Becker@ba-fk.verwalt-berlin.de
