---
title: "Open Government Data, Berlin Open Data"
date: "2024-12-22"
output: html_document
---

## Dataset: Suche nach anerkannten Veranstaltungen

In Berlin anerkannte Weiterbildungsveranstaltungen.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenarbeitweiterbildungbildungszeitsuche)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/arbeit/weiterbildung/bildungszeit/suche/)

Auto generated R starter code for data set a6828125-ae95-404f-9fb0-52eb91302fd8.

## Metadata

- **Maintainer** `n.n.`
- **Maintainer_email** `bildungszeit@senasgiva.berlin.de`
- **Tags** `['bildungszeit', 'simplesearch', 'weiterbildung', 'weiterbildungsveranstaltung']`
- **Date_released** `2015-10-19`
- **Metadata_created** `2023-11-01T14:01:17.996380`
- **Metadata_modified** `2024-12-22T00:28:38.083940`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a6828125-ae95-404f-9fb0-52eb91302fd8

df <- read.csv('https://www.berlin.de/sen/arbeit/weiterbildung/bildungszeit/suche/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

n.n. | bildungszeit@senasgiva.berlin.de
