---
title: "Open Government Data, Berlin Open Data"
date: "2025-01-26"
output: html_document
---

## Dataset: Berichte und Publikationen der OE QPK im Bezirksamt Mitte

Veröffentlichungen und Berichte der OE QPK im Bezirksamt Mitte von Berlin

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebamittepolitiku_bb0e906c99acea519db941ead230130e_ienstespublikationen)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-mitte/politik-und-verwaltung/service-und-organisationseinheiten/qualitaetsentwicklung-planung-und-koordination-des-oeffentlichen-gesundheitsdienstes/publikationen/)

Auto generated R starter code for data set a96fed5d-6890-49ef-baf5-1504a058fbc9.

## Metadata

- **Maintainer** `Svea Gille`
- **Maintainer_email** `svea.gille@ba-mitte.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2020-05-04`
- **Metadata_created** `2020-05-28T05:00:56.816627`
- **Metadata_modified** `2025-01-16T08:48:48.400228`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a96fed5d-6890-49ef-baf5-1504a058fbc9

df <- read.csv('https://www.berlin.de/ba-mitte/politik-und-verwaltung/service-und-organisationseinheiten/qualitaetsentwicklung-planung-und-koordination-des-oeffentlichen-gesundheitsdienstes/publikationen/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Svea Gille | svea.gille@ba-mitte.berlin.de
