---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-06"
output: html_document
---

## Dataset: Wahllokale zur Bundestagswahl 2013 in Berlin

Schl端ssel Wahlbezirk, Bezirksnummer, Wahlbezirksnummer, Lokal, Bezeichnung, PLZ, Ort, Anschrift, Zugang

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=wahllokale-zur-bundestagswahl-2013-in-berlin)<br>
[Direct link by Amt f端r Statistik Berlin-Brandenburg for dataset](https://www.statistik-berlin-brandenburg.de)

Auto generated R starter code for data set aa8ff09b-9da5-41f1-ac16-85ba424f9ead.

## Metadata

- **Maintainer** `Amt f端r Statistik Berlin-Brandenburg`
- **Maintainer_email** `info@statistik-bbb.de`
- **Tags** `['Wahllokale Berlin']`
- **Date_released** `2013-09-20`
- **Metadata_created** `2016-02-18T21:29:30.183994`
- **Metadata_modified** `2019-05-13T09:52:17.350516`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : aa8ff09b-9da5-41f1-ac16-85ba424f9ead

df <- read.csv('https://www.statistik-berlin-brandenburg.de/opendata/BTW2013_BE_Wahllokale_Schluessel.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Amt f端r Statistik Berlin-Brandenburg | info@statistik-bbb.de
