---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-02"
output: html_document
---

## Dataset: Publikationen des Bezirksamtes Steglitz-Zehlendorf

Diese Publikationsdatenbank enthält Publikationen des Bezirksamts Steglitz-Zehlendorf.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebasteglitzzehlendorfservicepublikationen)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-steglitz-zehlendorf/service/publikationen/)

Auto generated R starter code for data set ab9cc108-b6f1-4115-8169-68d9d793b484.

## Metadata

- **Maintainer** `Elisa Grundmann`
- **Maintainer_email** `internet@ba-sz.berlin.de`
- **Tags** `['broschüren', 'simplesearch']`
- **Date_released** `2020-02-18`
- **Metadata_created** `2020-02-18T13:47:44.871137`
- **Metadata_modified** `2024-09-18T16:30:10.109220`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ab9cc108-b6f1-4115-8169-68d9d793b484

df <- read.csv('https://www.berlin.de/ba-steglitz-zehlendorf/service/publikationen/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Elisa Grundmann | internet@ba-sz.berlin.de
