---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-16"
output: html_document
---

## Dataset: Übersicht über Wirtschaftsbereiche / Branchen



    Übersicht über Wirtschaftsbereiche / Branchen für die im
    Gemeinsamen Tarifregister Berlin und Brandenburg Tarifverträge
    vorliegen, aus denen Auskunft erteilt werden kann.
  


[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenarbeitberlin_f583ecdd542aaa626efa0019e98f500e_nwirtschaftsbereiche)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/arbeit/berlinarbeit-ziel-2/tarifregister/tarif-informationen/wirtschaftsbereiche/)

Auto generated R starter code for data set ae16b5cb-23d8-458e-be23-fa47b3261add.

## Metadata

- **Maintainer** `Anette Leiner`
- **Maintainer_email** `tarifregister@senaif.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2016-05-24`
- **Metadata_created** `2016-08-05T10:03:43.270217`
- **Metadata_modified** `2016-08-05T10:03:43.292830`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ae16b5cb-23d8-458e-be23-fa47b3261add

df <- read.csv('http://www.berlin.de/sen/arbeit/berlinarbeit-ziel-2/tarifregister/tarif-informationen/wirtschaftsbereiche/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Anette Leiner | tarifregister@senaif.berlin.de
