---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-31"
output: html_document
---

## Dataset: Parkscheinautomaten (PSA) Standorte öffentlich anzeigen

Es werden 2 maschinenlesbare Dateien mit den aktuellen Standorten der Parkscheinautomaten (PSA) im Bezirk Pankow bereitgestellt.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=parkscheinautomaten-psa-standorte-oeffentlich-anzeigen-1118550)<br>
[Direct link by Datenrubrik for dataset]()

Auto generated R starter code for data set aed9be10-6d6b-4211-8d6b-c84a91369533.

## Metadata

- **Maintainer** `Jonas Karehnke`
- **Maintainer_email** `jonas.karehnke@ba-pankow.berlin.de`
- **Tags** `['Berlin', 'Handyparken', 'Ordnungsamt', 'Pankow', 'Parkplatz', 'Parkraumbewirtschaftung', 'Parkscheinautomat', 'Parkticket', 'Ticket', 'parken']`
- **Date_released** `2021-08-23`
- **Metadata_created** `2021-08-23T08:43:25.840676`
- **Metadata_modified** `2021-09-27T08:26:53.339090`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : aed9be10-6d6b-4211-8d6b-c84a91369533

df <- read.csv('https://www.berlin.de/ba-pankow/service/daten/2021_09_27_parkscheinautomaten_pankow.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Jonas Karehnke | jonas.karehnke@ba-pankow.berlin.de
