---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-04"
output: html_document
---

## Dataset: Durch die Gemeinschaftsaufgabe 'Verbesserung der regionalen Wirtschaftsstruktur' (GRW) geförderte Projekte ab 2008

Durch die Gemeinschaftsaufgabe “Verbesserung der regionalen Wirtschaftsstruktur” (GRW) geförderte Projekte ab 2008

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschaftgruendenundfoerderninvestitionsfoerderungwachsengrwprojekte)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/wirtschaft/gruenden-und-foerdern/investitionsfoerderung/wachsen/grw-projekte/)

Auto generated R starter code for data set b721499a-88cd-458a-82d8-d90e17ff39b7.

## Metadata

- **Maintainer** `Maria Szeponik`
- **Maintainer_email** `maria.szeponik@senweb.berlin.de`
- **Tags** `['förderung', 'grw', 'infrastrukturförderung', 'simplesearch', 'unternehmensförderung']`
- **Date_released** `2019-06-18`
- **Metadata_created** `2019-09-14T14:39:45.671996`
- **Metadata_modified** `2024-08-07T20:21:22.585603`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : b721499a-88cd-458a-82d8-d90e17ff39b7

df <- read.csv('https://www.berlin.de/sen/wirtschaft/gruenden-und-foerdern/investitionsfoerderung/wachsen/grw-projekte/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Maria Szeponik | maria.szeponik@senweb.berlin.de
