---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-26"
output: html_document
---

## Dataset: Kfz-Kennzeichen Deutschland

Liste der deutschen Kfz-Kennzeichen (Stand Juli 2012)

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=kfz-kennzeichen-deutschland)<br>
[Direct link by Senatsverwaltung für Wirtschaft, Energie und Betriebe for dataset]()

Auto generated R starter code for data set be8c1bf6-50cf-4fab-8ea3-179ca947652a.

## Metadata

- **Maintainer** ``
- **Maintainer_email** `wolfgang.both@senwtf.berlin.de`
- **Tags** `['auto', 'fahrzeug', 'kennzeichen', 'kfz', 'verkehr']`
- **Date_released** `2012-12-11`
- **Metadata_created** `2016-02-18T20:46:43.083819`
- **Metadata_modified** `2020-09-25T17:03:24.391296`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : be8c1bf6-50cf-4fab-8ea3-179ca947652a

df <- read.csv('https://berlinonline.github.io/berlin-legacy-datasets/data/kfz-kennz-d.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

No contact information provided.
