---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-10"
output: html_document
---

## Dataset: Kamerale Monatsdaten Bezirksamt Marzahn-Hellersdorf 2016

Stand der Haushaltswirtschaft des Bezikes Marzahn-Hellersdorf von Berlin zum jeweiligen Monatsende je Kapitel und Titel

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=kamerale-monatsdaten-bezirksamt-marzahn-hellersdorf-2016)<br>
[Direct link by Bezirksamt Marzahn-Hellersdorf for dataset](http://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/service-und-organisationseinheiten/finanzen/)

Auto generated R starter code for data set be99fb4f-78ff-4550-8cb2-0adebbe39b06.

## Metadata

- **Maintainer** ``
- **Maintainer_email** `ilona.lutzke@ba-mh.berlin.de`
- **Tags** `['Kamerale Monatsdaten Bezirksamt Marzahn-Hellersdorf 2016']`
- **Date_released** `2016-04-05`
- **Metadata_created** `2016-04-05T09:53:39.987626`
- **Metadata_modified** `2016-11-17T12:02:57.437475`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : be99fb4f-78ff-4550-8cb2-0adebbe39b06

df <- read.csv('https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/service-und-organisationseinheiten/finanzen/kamerale-monatsdaten/kamerale_monatsdaten_jan_2016_csv.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

No contact information provided.
