---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-19"
output: html_document
---

## Dataset: Suche nach Gedenkorten in Treptow-Köpenick

Gedenkorte in Treptow-Köpenick

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindemuseumtreptowkoepenickgedenkortesuchenachgedenkorten)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/museum-treptow-koepenick/gedenkorte/suche-nach-gedenkorten/)

Auto generated R starter code for data set c76c5e40-cdac-4550-ae3e-99c7e2a3c5fc.

## Metadata

- **Maintainer** `Agathe Conradi`
- **Maintainer_email** `museum@ba-tk.berlin.de`
- **Tags** `['gedenken', 'gedenkkultur', 'gedenkort', 'gedenkstein', 'gedenktafel', 'simplesearch', 'stolperstein']`
- **Date_released** `2023-03-28`
- **Metadata_created** `2023-03-30T12:48:56.085848`
- **Metadata_modified** `2024-08-07T18:34:47.041125`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : c76c5e40-cdac-4550-ae3e-99c7e2a3c5fc

df <- read.csv('https://www.berlin.de/museum-treptow-koepenick/gedenkorte/suche-nach-gedenkorten/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Agathe Conradi | museum@ba-tk.berlin.de
