---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-15"
output: html_document
---

## Dataset: Gästebuch



[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindegleichstellungweiterdenkenkampagnegaestebuchdatenbankanwendung)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/gleichstellung-weiter-denken/kampagne/gaestebuch/datenbank-anwendung/)

Auto generated R starter code for data set c89168c3-8633-4bd1-b719-17dfcb127bd9.

## Metadata

- **Maintainer** `Sabrina Petersen`
- **Maintainer_email** `petersen@ariadne-an-der-spree.de`
- **Tags** `['simplesearch']`
- **Date_released** `2014-10-16`
- **Metadata_created** `2016-02-18T20:41:39.255077`
- **Metadata_modified** `2016-10-07T13:29:26.420962`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : c89168c3-8633-4bd1-b719-17dfcb127bd9

df <- read.csv('http://www.berlin.de/gleichstellung-weiter-denken/kampagne/gaestebuch/datenbank-anwendung/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Sabrina Petersen | petersen@ariadne-an-der-spree.de
