---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-26"
output: html_document
---

## Dataset: Straßenbaumfällungen in Steglitz-Zehlendorf

Eine Übersicht aller gefällten Bäume in Steglitz-Zehlendorf 2023

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebasteglitzzehle_ac744dfb0f27da6460b7f6bae42bde39_baeumebaumfaellungen)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-steglitz-zehlendorf/politik-und-verwaltung/aemter/strassen-und-gruenflaechenamt/gruenflaechen/baeume/baumfaellungen/)

Auto generated R starter code for data set cee8c73a-88a2-431b-9ed3-7b800a85e643.

## Metadata

- **Maintainer** `Romy Tempel`
- **Maintainer_email** `romy.tempel@ba-sz.berlin.de`
- **Tags** `['bäume', 'fällungen', 'simplesearch']`
- **Date_released** `2017-04-25`
- **Metadata_created** `2020-01-16T13:45:53.527462`
- **Metadata_modified** `2024-10-24T09:38:12.733487`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : cee8c73a-88a2-431b-9ed3-7b800a85e643

df <- read.csv('https://www.berlin.de/ba-steglitz-zehlendorf/politik-und-verwaltung/aemter/strassen-und-gruenflaechenamt/gruenflaechen/baeume/baumfaellungen/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Romy Tempel | romy.tempel@ba-sz.berlin.de
