---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-31"
output: html_document
---

## Dataset: Denkmalliste Berlin im CSV-Format

Denkmalliste Berlin im CSV-Format

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=denkmalliste-berlin-im-csv-format)<br>
[Direct link by Landesdenkmalamt for dataset](https://www.berlin.de/landesdenkmalamt/denkmale/liste-karte-datenbank/denkmalliste/erlaeuterung-651203.php)

Auto generated R starter code for data set d4ff12e7-e02a-4a14-a1d7-2d9dc0f143d8.

## Metadata

- **Maintainer** `Juliane Stamm`
- **Maintainer_email** `Juliane.Stamm@lda.Berlin.de`
- **Tags** `['Baudenkmale', 'Bodendenkmale', 'Denkmalbereiche', 'Denkmale', 'Denkmalliste', 'Denkmalpflege', 'Denkmalschutz', 'Denkmalverzeichnis', 'Ensembles', 'Ensembleteile', 'Gartendenkmale', 'Gesamtanlagen']`
- **Date_released** `2021-05-05`
- **Metadata_created** `2021-03-29T12:05:15.450361`
- **Metadata_modified** `2021-07-02T10:17:39.609333`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : d4ff12e7-e02a-4a14-a1d7-2d9dc0f143d8

df <- read.csv('https://www.berlin.de/landesdenkmalamt/_assets/pdf-und-zip/denkmale/liste-karte-datenbank/denkmalliste_berlin.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Juliane Stamm | Juliane.Stamm@lda.Berlin.de
