---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-27"
output: html_document
---

## Dataset: Energieverbrauchsübersicht bezirklicher Gebäude 2017 - Bezirk Mitte

Hiermit erhalten Sie die Energieverbrauchsübersicht der Liegenschaften in Berlin Mitte 2017

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=energieverbrauchsuebersicht-berlin-mitte-2017)<br>
[Direct link by Datenrubrik for dataset]()

Auto generated R starter code for data set da90cefc-03fe-438f-b989-d80f98ead12a.

## Metadata

- **Maintainer** `Frau Unterberg`
- **Maintainer_email** `lisa.unterberg@ba-mitte.berlin.de`
- **Tags** `['Energie', 'Energieverbrauch']`
- **Date_released** `2019-01-23`
- **Metadata_created** `2019-02-18T14:20:20.984606`
- **Metadata_modified** `2020-03-19T13:19:42.816825`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : da90cefc-03fe-438f-b989-d80f98ead12a

df <- read.csv('https://www.berlin.de/ba-mitte/service/daten/verbrauchsuebersicht_bami_2017_pressestelle_opendata.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Frau Unterberg | lisa.unterberg@ba-mitte.berlin.de
