---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-18"
output: html_document
---

## Dataset: Einwohnerinnen und Einwohner in den Ortsteilen Berlins am 31.12.2018

Einwohnerinnen und Einwohner in den Ortsteilen Berlins am 31.12.2018

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=einwohnerinnen-und-einwohner-in-den-ortsteilen-berlins-am-31-12-2018)<br>
[Direct link by Amt für Statistik Berlin-Brandenburg for dataset](https://www.statistik-berlin-brandenburg.de)

Auto generated R starter code for data set da967115-f046-4333-be53-ada9c9145978.

## Metadata

- **Maintainer** `Amt für Statistik Berlin-Brandenburg`
- **Maintainer_email** `einwohner@statistik-bbb.de`
- **Tags** `['Einwohner', 'Ortsteile']`
- **Date_released** `2019-05-29`
- **Metadata_created** `2019-05-29T07:17:47.000970`
- **Metadata_modified** `2019-05-29T07:18:57.441196`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : da967115-f046-4333-be53-ada9c9145978

df <- read.csv('https://www.statistik-berlin-brandenburg.de/opendata/EWR_Ortsteile_2018-12-31.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Amt für Statistik Berlin-Brandenburg | einwohner@statistik-bbb.de
