---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-04"
output: html_document
---

## Dataset: Einwohnerinnen und Einwohner in den Ortsteilen Berlins am 31.12.2012

Einwohnerinnen und Einwohner in den Ortsteilen Berlins am 31.12.2012

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=einwohnerinnen-und-einwohner-in-den-ortsteilen-berlins-am-31-12-2012)<br>
[Direct link by Amt f체r Statistik Berlin-Brandenburg for dataset](https://www.statistik-berlin-brandenburg.de)

Auto generated R starter code for data set daa1ba6d-9ff7-406c-865b-dae557e0184f.

## Metadata

- **Maintainer** `Amt f체r Statistik Berlin-Brandenburg`
- **Maintainer_email** `einwohner@statistik-bbb.de`
- **Tags** `['Einwohner', 'Ortsteile', 'kleinr채umige Einwohnerzahl']`
- **Date_released** `2013-06-19`
- **Metadata_created** `2016-02-18T21:08:58.214939`
- **Metadata_modified** `2019-05-13T09:59:36.845258`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : daa1ba6d-9ff7-406c-865b-dae557e0184f

df <- read.csv('https://www.statistik-berlin-brandenburg.de/opendata/EWR_Ortsteile_2012-12-31.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Amt f체r Statistik Berlin-Brandenburg | einwohner@statistik-bbb.de
