---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-23"
output: html_document
---

## Dataset: Trinkbrunnen in Steglitz-Zehlendorf

Liste der öffentlichen Trinkbrunnen im Bezirk Steglitz-Zehlendorf.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=oeffentliche-trinkbrunnen-in-steglitz-zehlendorf-1346307)<br>
[Direct link by Datenrubrik for dataset]()

Auto generated R starter code for data set e36a2425-8dae-4c96-8b23-7f06471ddf93.

## Metadata

- **Maintainer** ``
- **Maintainer_email** `internet@ba-sz.berlin.de`
- **Tags** `['Gesundheit', 'Hitze', 'Trinkbrunnen', 'Wasser']`
- **Date_released** `2023-07-17`
- **Metadata_created** `2023-07-21T12:57:01.042600`
- **Metadata_modified** `2023-07-25T07:26:04.572245`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : e36a2425-8dae-4c96-8b23-7f06471ddf93

df <- read.csv('https://www.berlin.de/ba-steglitz-zehlendorf/service/daten/trinkbrunnen-in-steglitz-zehlendorf.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

No contact information provided.
