---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-17"
output: html_document
---

## Dataset: Adressen Kindertagespflegestellen Steglitz-Zehlendorf

Adressen Kindertagespflegestellen In Steglitz – Zehlendorf

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebasteglitzzehle_0d54329293fd46386072c5c26c8e51d9_ngtagespflegestellen)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-steglitz-zehlendorf/politik-und-verwaltung/aemter/jugendamt/angebote-fuer-kinder-jugendliche-und-familien/kinderbetreuung/tagespflegestellen/)

Auto generated R starter code for data set e7b4e3f5-3c8e-417a-9396-387373020ff2.

## Metadata

- **Maintainer** `Peter Hartmann`
- **Maintainer_email** `peter.hartmann@ba-sz.berlin.de`
- **Tags** `['simplesearch', 'umkreissuche_tagespflege_tagespflegeplätze']`
- **Date_released** `2017-03-07`
- **Metadata_created** `2017-03-09T13:23:04.533466`
- **Metadata_modified** `2024-08-13T05:36:10.580417`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : e7b4e3f5-3c8e-417a-9396-387373020ff2

df <- read.csv('https://www.berlin.de/ba-steglitz-zehlendorf/politik-und-verwaltung/aemter/jugendamt/angebote-fuer-kinder-jugendliche-und-familien/kinderbetreuung/tagespflegestellen/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Peter Hartmann | peter.hartmann@ba-sz.berlin.de
