---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-15"
output: html_document
---

## Dataset: Aktenplan der Senatsverwaltung für Bildung, Jugend und Familie

Aktenplan der Senatsverwaltung für Bildung, Jugend und Familie auf der Grundlage des Aktenplans für die Bildungsverwaltung.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenbjfueberunsaktenplan)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/bjf/ueber-uns/aktenplan/)

Auto generated R starter code for data set ec0ae642-8a35-43d7-b260-4fc8e55aec71.

## Metadata

- **Maintainer** `Berlin.de`
- **Maintainer_email** `open-data@senbjf.berlin.de`
- **Tags** `['aktenplan', 'simplesearch']`
- **Date_released** `2022-05-04`
- **Metadata_created** `2024-02-01T11:26:55.566907`
- **Metadata_modified** `2024-08-07T19:53:11.349651`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ec0ae642-8a35-43d7-b260-4fc8e55aec71

df <- read.csv('https://www.berlin.de/sen/bjf/ueber-uns/aktenplan/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Berlin.de | open-data@senbjf.berlin.de
