---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-27"
output: html_document
---

## Dataset: Übersicht der Beschlüsse des Bezirksamts Steglitz-Zehlendorf

Hier finden Sie Protokolle, Vorlagen und Beschlüsse der Sitzungen des Bezirksamts Steglitz-Zehlendorf

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebasteglitzzehlendorfpolitikundverwaltungbezirksamtprotokolle2019)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-steglitz-zehlendorf/politik-und-verwaltung/bezirksamt/protokolle/2019/)

Auto generated R starter code for data set ec265a94-7e81-4e78-ad26-4bd32bf29ebc.

## Metadata

- **Maintainer** `Elisa Grundmann`
- **Maintainer_email** `internet@ba-sz.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2018-10-26`
- **Metadata_created** `2019-08-20T14:22:46.815536`
- **Metadata_modified** `2023-09-14T15:56:45.423952`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ec265a94-7e81-4e78-ad26-4bd32bf29ebc

df <- read.csv('https://www.berlin.de/ba-steglitz-zehlendorf/politik-und-verwaltung/bezirksamt/protokolle/2019/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Elisa Grundmann | internet@ba-sz.berlin.de
