---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-28"
output: html_document
---

## Dataset: RBS-Adressen, Dezember 2014

RBS-Adressen, 
Dezember 2014

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=rbs-adressen-dezember-2014)<br>
[Direct link by Amt für Statistik Berlin-Brandenburg for dataset](https://www.statistik-berlin-brandenburg.de)

Auto generated R starter code for data set ed664660-a2f3-49f2-9a8d-af23ee7438f1.

## Metadata

- **Maintainer** `Amt für Statistik Berlin-Brandenburg`
- **Maintainer_email** `info@statistik-bbb.de`
- **Tags** `['Adressen', 'RBS', 'RBS-Adressen', 'Straßenschlüssel']`
- **Date_released** `2015-02-06`
- **Metadata_created** `2016-02-18T20:41:15.467278`
- **Metadata_modified** `2019-05-13T09:44:40.675628`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ed664660-a2f3-49f2-9a8d-af23ee7438f1

df <- read.csv('https://www.statistik-berlin-brandenburg.de/opendata/RBS_OD_ADR.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Amt für Statistik Berlin-Brandenburg | info@statistik-bbb.de
