---
title: "Open Government Data, Berlin Open Data"
date: "2025-01-26"
output: html_document
---

## Dataset: Aktuell geförderte Projekte

Aktuell geförderte ESF-Projekte

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschaftgr_db438ad42929c3cdb4b41c079ef44731_lgefoerderteprojekte)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/wirtschaft/gruenden-und-foerdern/europaeische-strukturfonds/esf-foerderperiode-2014-2020/aktuell-gefoerderte-projekte/)

Auto generated R starter code for data set f2d66411-3c41-4b4c-83b5-6b9b20f94fcc.

## Metadata

- **Maintainer** `Ralf Eberhardt`
- **Maintainer_email** `ralf.eberhardt@senweb.berlin.de`
- **Tags** `['esf', 'eu', 'simplesearch']`
- **Date_released** `2020-01-22`
- **Metadata_created** `2021-09-04T15:29:07.333259`
- **Metadata_modified** `2023-05-25T15:29:08.013473`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f2d66411-3c41-4b4c-83b5-6b9b20f94fcc

df <- read.csv('https://www.berlin.de/sen/wirtschaft/gruenden-und-foerdern/europaeische-strukturfonds/esf-foerderperiode-2014-2020/aktuell-gefoerderte-projekte/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Ralf Eberhardt | ralf.eberhardt@senweb.berlin.de
