---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-01"
output: html_document
---

## Dataset: Berliner und Brandenburger Weihnachtsmärkte

Berliner Weihnachtsmärkte

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwebservicemaerktefesteweihnachtsmaerkte)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/sen/web/service/maerkte-feste/weihnachtsmaerkte/)

Auto generated R starter code for data set f41253a7-38a7-4d26-ae7c-17ffe7b5557a.

## Metadata

- **Maintainer** `Berlin.de`
- **Maintainer_email** `Abdulkadir.Dagci@senweb.berlin.de`
- **Tags** `['simplesearch', 'weihnachtsmarkt']`
- **Date_released** `2014-10-17`
- **Metadata_created** `2017-10-23T09:05:26.711193`
- **Metadata_modified** `2024-10-21T07:49:34.226106`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f41253a7-38a7-4d26-ae7c-17ffe7b5557a

df <- read.csv('https://www.berlin.de/sen/web/service/maerkte-feste/weihnachtsmaerkte/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Berlin.de | Abdulkadir.Dagci@senweb.berlin.de
