---
title: "Open Government Data, Berlin Open Data"
date: "2025-02-09"
output: html_document
---

## Dataset: Bezirksamtsbeschlüsse

Zur Veröffentlichung freigegebene Bezirksamtsbeschlüsse des Bezirksamts Treptow-Köpenick

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebatreptowkoepenickpolitikundverwaltungbezirksamtbeschluessesimplesearch)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-treptow-koepenick/politik-und-verwaltung/bezirksamt/beschluesse/simple-search/)

Auto generated R starter code for data set f4b9fe4a-003c-4bcd-848f-d7de5dc34ed6.

## Metadata

- **Maintainer** `Büro des Bezirksbürgermeisters`
- **Maintainer_email** `sabrina.kirmse@ba-tk.berlin.de`
- **Tags** `['ba-beschluss', 'ba-beschlüsse', 'simplesearch']`
- **Date_released** `2014-06-23`
- **Metadata_created** `2016-02-18T20:50:29.705325`
- **Metadata_modified** `2024-11-06T10:21:28.872135`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f4b9fe4a-003c-4bcd-848f-d7de5dc34ed6

df <- read.csv('https://www.berlin.de/ba-treptow-koepenick/politik-und-verwaltung/bezirksamt/beschluesse/simple-search/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Büro des Bezirksbürgermeisters | sabrina.kirmse@ba-tk.berlin.de
