---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-06"
output: html_document
---

## Dataset: Beschäftigungsdaten für OpenData



    Erwerbstätige in Berlin nach Wirtschaftsbereichen
  


[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindesenwirtschaftwi_01465ef61ac798a6d4b313be6150d040_atenbeschaeftigungod)<br>
[Direct link by SimpleSearch for dataset](http://www.berlin.de/sen/wirtschaft/wirtschaft-und-technologie/konjunktur-und-statistik/wirtschaftsdaten/beschaeftigung/od/)

Auto generated R starter code for data set f7562b18-8420-499b-9dab-aee642477712.

## Metadata

- **Maintainer** `Ralf Eberhardt`
- **Maintainer_email** `ralf.eberhardt@senwtf.berlin.de`
- **Tags** `['simplesearch']`
- **Date_released** `2015-01-29`
- **Metadata_created** `2016-02-18T21:26:41.125537`
- **Metadata_modified** `2016-02-18T21:26:41.139121`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f7562b18-8420-499b-9dab-aee642477712

df <- read.csv('http://www.berlin.de/sen/wirtschaft/wirtschaft-und-technologie/konjunktur-und-statistik/wirtschaftsdaten/beschaeftigung/od/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Ralf Eberhardt | ralf.eberhardt@senwtf.berlin.de
