---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-08"
output: html_document
---

## Dataset: Doppelhaushalt 2024/2025 (2.Nachtrag)

Der 2. Nachtrag des Haushaltsplans 2024/2025 bietet einen Überblick über die geplanten Ausgaben und Einnahmen des Landes Berlin.

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=doppelhaushalt-2024-2025-2-nachtrag-1468058)<br>
[Direct link by Datenrubrik for dataset]()

Auto generated R starter code for data set fa1801a0-212e-44f3-9d76-f020f19a135e.

## Metadata

- **Maintainer** `Julia Schabos`
- **Maintainer_email** `julia.schabos@senfin.berlin.de`
- **Tags** `['Haushaltsplan', 'Landeshaushalt']`
- **Date_released** `2024-07-17`
- **Metadata_created** `2024-07-17T08:45:48.744243`
- **Metadata_modified** `2024-10-02T11:18:34.752575`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : fa1801a0-212e-44f3-9d76-f020f19a135e

df <- read.csv('https://www.berlin.de/sen/finanzen/service/daten/doppelhaushalt_24_25_2_nachtrag.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Julia Schabos | julia.schabos@senfin.berlin.de
