---
title: "Open Government Data, Berlin Open Data"
date: "2024-11-11"
output: html_document
---

## Dataset: Datenportal Jahresrückblick 2018

Welche Datensätze wurden im Berliner Portal für Offene Daten daten.berlin.de im Jahr 2018 am häufigsten nachgefragt?

Alle Daten und Code gibt es auch [auf Github](https://github.com/berlinonline/berlin-open-data-stats-2018).

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=datenportal-jahresruckblick-2018)<br>
[Direct link by BerlinOnline Stadtportal GmbH for dataset](https://daten.berlin.de/interaktion/artikel/jahresrueckblick-2018)

Auto generated R starter code for data set fb25520a-713c-4185-b445-8282ec344dc5.

## Metadata

- **Maintainer** `Knud Möller`
- **Maintainer_email** `opendata@berlin.de`
- **Tags** `['datenportal', 'open data', 'page impressions', 'page view', 'portal', 'statistics', 'usage']`
- **Date_released** `2019-01-07`
- **Metadata_created** `2019-01-07T14:00:11.919236`
- **Metadata_modified** `2024-10-18T06:40:25.900390`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : fb25520a-713c-4185-b445-8282ec344dc5

df <- read.csv('https://raw.githubusercontent.com/berlinonline/berlin-open-data-stats-2018/master/daten_berlin_de.page_stats.datensaetze.summed.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Knud Möller | opendata@berlin.de
