---
title: "Open Government Data, Berlin Open Data"
date: "2024-10-29"
output: html_document
---

## Dataset: Kindertagespflegestellen in Marzahn-Hellersdorf

Kindertagespflegestellen in Marzahn-Hellersdorf

[Direct link by Berlin Open Data for dataset](https://datenregister.berlin.de/api/3/action/package_show?id=simple_search_wwwberlindebamarzahnheller_6ccf5674c0f4ae4505230803a4d5a431_ungkindertagespflege)<br>
[Direct link by SimpleSearch for dataset](https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/betreuung-und-bildung/kindertagespflege/)

Auto generated R starter code for data set ff461bf8-a586-4b50-96d1-93b5ed78d487.

## Metadata

- **Maintainer** `Viktoria Funk`
- **Maintainer_email** `viktoria.funk@ba-mh.berlin.de`
- **Tags** `['kindertagespflegestellen_in_marzahn-hellersdorf', 'simplesearch']`
- **Date_released** `2014-12-29`
- **Metadata_created** `2019-03-19T23:07:41.071542`
- **Metadata_modified** `2024-10-07T07:27:44.150994`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ff461bf8-a586-4b50-96d1-93b5ed78d487

df <- read.csv('https://www.berlin.de/ba-marzahn-hellersdorf/politik-und-verwaltung/aemter/jugendamt/betreuung-und-bildung/kindertagespflege/index.php/index/all.csv?q=')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

Viktoria Funk | viktoria.funk@ba-mh.berlin.de
